### 2018-09-28 paper.tex
Wip

\begin{figure}
  \begin{lstlisting}[]
  Usage: guild run [OPTIONS] cnn:train
  [FLAG]...

@@

@@

\subsection{Testing models}

@@

>>>>

\begin{figure}
  \begin{lstlisting}
  Usage: guild run [OPTIONS] cnn:train
  [FLAG]...

@@

\subsection{Isolating Runs Using Environments}

The discussion of using models to this point has not mentioned
\emph{environments} as environment are optional for using Guild
AI. However, environments are useful for isolating installed packages
and runs on a system.

When running Guild AI operations in an activated environment, the
following are environment specific:

\begin{itemize}
\item Installed packages and therefore installed models
\item Runs
\end{itemize}

Environments are created using the \verb|guild init| command. Once
created, an environment must be explicitly activated using the
\verb|source guild-env| command.

Environments are useful isolating project level work. It's not uncommon
to have separate environments for each project.

@@

\subsection{Testing}

Users may trust that installed packages have undergone testing before
they being published. The goal of managing machine learning models as
packages, after all, is to ensure that models work as advertised. In
support of this goal, Guild AI lets developers and packagers specify
tests that can be used to model integrity.

Listing~\ref{lst:tests} contains two tests: one that verifies model
help---ensuring that what the user sees when she runs
\verb|guild help| is what the developer intendes---and another that
exercises model operations and checks results.

\begin{lstlisting}[
    caption=Model tests,
    label={lst:tests}]
- test: help
  steps:
    - compare-help: test/help
- test: model
  steps:
    - run-op: prepare-samples
      flags:
        images: test/samples
    - run-op: train
      expected:
        - file: checkpoint
    - run-op: evaluate
      expected:
        - scalar: accuracy > 0.7
\end{lstlisting}

The model test runs three operations: prepare-samples, train, and
evaluate. The train step asserts that a checkpoint file exist, which
confirms that the operation successfully saved a checkpoint. The
evaluate step asserts that the accuracy for the trained model is at
least 0.7.

Tests can be run using the \verb|guild test| command.

Tests may be run on an ad hoc basis or as a continuous integration
release process.

@@

Our final point of discussion on the topic of model development is
\emph{packaging}. Packaging consists of generating a Python wheel
distribution that contains the Guild file and all supporting project
code. The generated wheel distribution may be distributed internally
within an organization or published to PyPI.

Packages that are published to PyPI can be installed using the command
\verb|guild install| or using pip.

Packages are convenient for installing
